An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-05-02 Article/EconGrowth2.Rnw
Added argument names to unz function.
Beginning the process of getting the paper to build after refactoring EconData.

# Set up for loading resample results
# We need to define a directory path from "Article" to the resample data results
archive <- file.path("..", "data_resample_2014-04-29_Refactored-EconData_n=2.zip")
# baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# Load the fits to the original historical data out of the archive we're using.
# This object (oModels) should be passed in to functions that need information from orig fits.
f <- gzcon(unz(archive, file.path("oModels.Rdata")))
oModels <- readRDS(f)
close(f)

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
data <- loadResampledData(archive=archive, 
                          country=countryAbbrevs, 
                          model="cd", 
                          factors=c("iK+iL", "iK+iL+iQ"), 
                          prefix="coeffs")
# Rearrange the factors to obtain our preferred ordering of countries.
for (l in rev(countryAbbrevs)) { data$countryAbbrev <- relevel(data$countryAbbrev, ref=l) }
# Replace all NA's in energyType with "none"

# Rearrange the factors to obtain our preferred ordering of countries.

for (l in rev(energyTypes)) { data$energyType <- relevel(data$energyType, ref=l) }
standardTriPlot(data=data, facet_formula=countryAbbrev~energyType)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
cdData <- loadCDSpaghettiGraphData(energyType="none", baseHistorical=baseHistorical, baseResample=baseResample)
cdQData <- loadCDSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
cdData <- rbind(cdData, cdQData)
spaghettiPlot(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

>>>>

# Set up for loading resample results
# We need to define a directory path from "Article" to the resample data results
archive <- file.path("..", "data_resample_2014-05-01_Refactored-EconData_n=1000.zip")
# baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# Load the fits to the original historical data out of the archive we're using.
# This object (oModels) should be passed in to functions that need information from orig fits.
f <- gzcon(unz(description=archive, filename=file.path("oModels.Rdata")))
oModels <- readRDS(f)
close(f)

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
data <- loadResampledData(archive=archive, 
                          country=countryAbbrevs, 
                          model="cd", 
                          factors=c("iK+iL", "iK+iL+iQ"), 
                          kind="coeffs")
# Rearrange the factors to obtain our preferred ordering of countries.
# for (lev in rev(countryAbbrevs)) { data$country <- relevel(data$country, ref=lev) }
# Replace all NA's in energyType with "none"

# Rearrange the factors to obtain our preferred ordering of energy types.
# for (lev in rev(energyTypes)) { data$energy <- relevel(data$energy, ref=lev) }
standardTriPlot(data=data, facet_formula=country~energy)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
# cdData <- loadCDSpaghettiGraphData(energyType="none", baseHistorical=baseHistorical, baseResample=baseResample)
# cdQData <- loadCDSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
# cdData <- rbind(cdData, cdQData)
cdData <- loadResampledData(archive=archive, country=countryAbbrevs, model="cd", factors=c("iK+iL", "iK+iL+iQ"), kind="fitted")
spaghettiPlot(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}
